An efficient audio coding scheme for quantitative and qualitative large scale acoustic monitoring using the sensor grid approach

### 2017-10-17 paper/article.tex
web update

The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/web/examples.html}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance. Given the test conditions presented in Section~\ref{sec:inintelligibility} and the number of subjects, the mean and standard deviation are computed on an average of 54 results per frame rate parameter: 12 subjects evaluating each analysis resolution 4.5 times on average.

>>>>

The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance. Given the test conditions presented in Section~\ref{sec:inintelligibility} and the number of subjects, the mean and standard deviation are computed on an average of 54 results per frame rate parameter: 12 subjects evaluating each analysis resolution 4.5 times on average.
